Verifying Demonstrations

### 2018-06-11 paper/DB-anon-cred.tex

\ProvideDocumentCommand{\PPK}{o o}{\ensuremath{%
    \operatorname{PPK}%
    \IfValueT{#1}{%
      \IfValueTF{#2}{%
        \mleft\{\mleft(#1\mright) : #2\mright\}%
      }{%
        \mleft\{#1\mright\}%
      }%
    }%
  }}

@@

\NewScheme{\DBS}{DBS}
\NewAlgorithm{\DBSprove}{\DBS.\!Prove}
\NewAlgorithm{\DBSverify}{\DBS.\!Verify}

\emph{Reattempting a distance-bounding Schnorr protocol.}
In the original \ac{DB} paper by \citet{DistanceBounding}, one of the distance-bounding protocol is based on the Schnorr identification scheme~\cite{Schnorr}.
However, this \ac{DB} Schnorr protocol was shown to be prone to distance hijacking~\cite{DistanceHijacking}, in addition of also not being secure against terrorist fraud either.
We now propose another way to turn the Schnorr protocol into a public-key \iac{DB} protocol which is secure against \ac{DBMF}, \ac{DBDF}, \ac{DBDH}, \ac{DBTF} and an impersonating verifier.

>>>>

@@

\emph{Reattempting a distance-bounding Schnorr protocol.}%
\label{DBSchnorr}
In the original \ac{DB} paper by \citet{DistanceBounding}, one of the distance-bounding protocol is based on the Schnorr identification scheme~\cite{Schnorr}.
However, this \ac{DB} Schnorr protocol was shown to be prone to distance hijacking~\cite{DistanceHijacking}, in addition of also not being secure against terrorist fraud either.
We now propose another way to turn the Schnorr protocol into a public-key \iac{DB} protocol which is secure against \ac{DBMF}, \ac{DBDF}, \ac{DBDH}, \ac{DBTF} and an impersonating verifier.

### 2018-06-11 paper/RelatedWork.tex

The seemingly most commonly used method for counting crowds at protests is \emph{Jacobs's method}~\cite{2016DemonstrationsInSeoul,BBCHowToCountProtestNumbers,HowWillWeKnowTrumpInauguralCrowdSize,TheXManMarch,TheCrowdNumbersGame}.
This manual method devised in the 1960s relies on aerial pictures of the event.
The verifier divides the protest venue into regions and then estimates the density of the crowd in the different regions before summing them up to get an estimate of the global count.
Clearly, this method is prone to errors as it is based on estimates.
It provides universal verifiability (\cref{UniversalVerif}) since anyone can redo the counting using the same pictures.
However, it is difficult to achieve individual verifiability (\cref{IndividualVerif}) using this method since it is hard to verify that oneself is indeed in any of the photos\footnote{It is of course possible with very detailed photos, but not currently realistic to do with aerial pictures.}.
We can argue that it also achieves eligibility (\cref{EligibilityVerif}) if all the photos are taken at the same point in time with no overlap, since then no one can be counted twice.
Unfortunately, we can only get the peak participation with this method.
When it comes to spatial and temporal eligibility, we have to rely on pictures (\eg by determining from the photos themselves when and where the they were taken).
However, this is prone to cheating --- and subject to a variety of manipulation techniques --- and the best we can do is to employ forensic methods to try to detect any modifications or other attempts of fraud.
From a privacy perspective, all techniques based on photo or video material are necessarily not privacy-preserving unless the protesters take actions to protect themselves.
For instance, there is a risk that participants are recognizable from the material if they do not wear masks.

@@

@@

Another related approach based on devices is UrbanCount~\cite{UrbanCount}, which relies on epidemic spreading of crowd-size estimates by device-to-device communication to count crowds in dense urban environments with high node-mobility and churn.
However, there is no consideration of a potentially adversarial setting and thus no verification or checks on eligibility.  DiVote~\cite{DiVote}, a prior work by the same authors for polling in dense areas, avoids double counting, but again only work withhonest participants.

Trusted infrastructure, for example deployed by a collection of  media outlets ~\cite{LeMondeProtestingSolution}, is another recent development, but without verfiability or privacy guarantees.

>>>>

The seemingly most commonly used method for counting crowds at protests is \emph{Jacobs's method}~\cite{2016DemonstrationsInSeoul,BBCHowToCountProtestNumbers,HowWillWeKnowTrumpInauguralCrowdSize,TheXManMarch,TheCrowdNumbersGame}.
This manual method devised in the 1960s relies on aerial pictures of the event.
The verifier divides the protest venue into regions and then estimates the density of the crowd in the different regions before summing them up to get an estimate of the global count.
Clearly, this method is prone to errors as it is based on estimates.
It provides universal verifiability (\cref{UniversalVerif}) since anyone can redo the counting using the same pictures.
However, it is difficult to achieve individual verifiability (\cref{IndividualVerif}) using this method since it is hard to verify that oneself is indeed in any of the photos\footnote{It is of course possible with very detailed photos, but not currently realistic to do with aerial pictures.}.
We can argue that it also achieves eligibility (\cref{EligibilityVerif}) if all the photos are taken at the same point in time with no overlap, since then no one can be counted twice.
Unfortunately, we can only get the peak participation with this method.
When it comes to spatial and temporal eligibility, we have to rely on pictures (\eg by determining from the pictures themselves when and where the they were taken).
However, this is prone to cheating --- and subject to a variety of manipulation techniques --- and the best we can do is to employ forensic methods to try to detect any modifications or other attempts of fraud.
From a privacy perspective, all techniques based on photo or video material are necessarily not privacy-preserving unless the protesters take actions to protect themselves.
For instance, there is a risk that participants are recognizable from the material if they do not wear masks.

@@

An approach that relies on a trusted infrastructure was recently deployed by a collection of media outlets to count protesters passing the line defined by a trusted sensor on marches~\cite{LeMondeProtestingSolution}, is another recent development. 
This solution does not offer strong verifiability guarantees and thus has complemented by micro-counts made by humans to estimate his margin of error.

@@

Another related approach based on devices is UrbanCount~\cite{UrbanCount}, which relies on epidemic spreading of crowd-size estimates by device-to-device communication to count crowds in dense urban environments with high node-mobility and churn.
However, there is no consideration of a potentially adversarial setting and thus no verification or checks on eligibility.  DiVote~\cite{DiVote}, a prior work by the same authors for polling in dense areas, avoids double counting, but again only work with honest participants.
